Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-10 Papers/ms.tex
Comparison with Brewer 2011
More entries in the table

\citet{2011MNRAS.412.2521B} argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models.

The source and the lens can be built up from a mixture of a moderate
number (from a few to a few hundred) of
simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is
dark \citep{2006ApJ...637..608B}.

@@

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
$W_{\rm src}$ &		Typical width of source blobs	& \\
$W_{\rm lens}$&		Typical width of lens blobs	& \\
{\bf Lens Blob Parameters}\\
$(x_i^{\rm src}, y_i^{\rm src})$
$M_i$  &
$v_i$  &
{\bf Source Blob Parameters}\\
{\bf Smooth Lens Parameters}\\
{\bf Noise Parameters}\\
{\bf Data}\\
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}

>>>>

\citet{2011MNRAS.412.2521B} argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models.
The source and the lens can be built up from a mixture of a moderate
number (from a few to a few hundred) of
simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is
dark \citep{2006ApJ...637..608B}. The main differences between the
\citet{2011MNRAS.412.2521B} and that of the present approach are:
i) we use a simpler and faster basis set, and ii) we apply it to the lens
as well as the source. However, in the present paper we do not account for
multi-band data.

@@

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & \\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs &\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & \\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& \\
$\mu_{\rm src}$ &	Typical flux of source blobs	& \\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& \\
$W_{\rm src}$ &		Typical width of source blobs	& \\
$W_{\rm lens}$&		Typical width of lens blobs	& \\
{\bf Source Blob Parameters}\\
$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & \\
$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
$w_i$  & Blob width & Exponential(mean=$W_{\rm src}$)\\
{\bf Lens Blob Parameters}\\
$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & \\
$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
$v_i$  & Blob width & Exponential(mean=$W_{\rm lens}$)\\
{\bf Smooth Lens Parameters}\\
{\bf Noise Parameters}\\
{\bf Data}\\
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}
